\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2017-05-31 graph_abs.tex
.

The abstraction of the hybrid dynamical system is a a
partitioning of the hybrid state space $\HybridStates$ into hyper-rectangles or cells $C_i \in \Cells$. The cells are
pairwise disjoint $C_i \cap C_j \neq \emptyset$ iff $i \neq j$ and
their union $\bigcup_{C_i\in\Cells}C_i$ is the state space $\HybridStates$. The partitions over
the continuous state space are implicitly defined using a quantization
function $Q_\epsilon$ parameterized by the precision $\epsilon$.
This further defines an equivalence relations such that $(\vx_i)
\equiv (\vx_j) \;\text{iff}\; Q_\epsilon(\vx_i) = Q_\epsilon(\vx_j)$.
In other words, $(\vx_i) \in C_i \; \text{iff} \; C_i = Q_\epsilon(\vx_i)$.

>>>>

The abstraction of the hybrid dynamical system is a a partitioning of
the hybrid state space $\HybridStates$ into hyper-rectangles or cells
$C_i \in \Cells$. The cells are pairwise disjoint $C_i \cap C_j \neq
\emptyset$ iff $i \neq j$ and their union $\bigcup_{C_i\in\Cells}C_i$
is the state space $\HybridStates$. The partitions over the continuous
state space are implicitly defined using a quantization function
$Q_\epsilon$ parameterized by the precision $\epsilon$.  This further
defines an equivalence relations such that $(\vx_i) \equiv (\vx_j)
\;\text{iff}\; Q_\epsilon(\vx_i) = Q_\epsilon(\vx_j)$.  In other
words, $(\vx_i) \in C_i \; \text{iff} \; C_i = Q_\epsilon(\vx_i)$. The
abstraction can be interpreted as a graph and explored using fixed
time $(\Delta\in\Reals^+)$ relations obtained using
$\simulate(\vx)$~\footnote{$\simulate(\vx)$ is a fixed
parameterization of $\mathsc{sim}(\vx,\Delta)$}.
